---
title: "p8105_hw1_th3072"
Author: Tianyou He
output: github_document
date: "2023-09-20"
---

```{r}
library(moderndive)
library(tidyverse)
data("early_january_weather")
```

##Problem 1

### Size of the Dataset:
```{r}
nrow(early_january_weather)
ncol(early_january_weather)
```
### Mean of temp
```{r}
mean(early_january_weather$temp)
```
**Answer**

`1. Variable of Dataset: day, hour, temp, dewp,humid,wind_dir, wind_speed,wind_gust,precip, pressure, visib, time_hour`

`2. The Size of Dataset: row = 358; column = 15`

`3. Mean temperature = 39.58212`

### Scatterplot of time_hour and temp
```{r yx_scatter}
ggplot(early_january_weather, aes(x = time_hour, y = temp, color = "humid" )) + geom_point()
ggsave("Problem_1_scatter.pdf")
```

`As can be seen from the scatterplot, the temperature tends to increase over time.`

##Problem 2

###Creat a data frame
```{r}
random_sample = rnorm(10)

logical_vector <- random_sample > 0

character_vector <- letters[1:10]

factor_vector <- factor(rep(c("red", "green","blue"), times = c(4,2,4)))
```

```{r}
df <- data.frame(random_sample, logical_vector, character_vector, factor_vector)
```

### Mean of each vector
```{r}
mean(random_sample)
mean(pull(df,logical_vector))
mean(pull(df,character_vector))
mean(pull(df,factor_vector))
```

### Change each vector into numeric vector
```{r}
numeric_logical <- as.numeric(logical_vector)
numeric_character <- as.numeric(character_vector)
numeric_factro <- as.numeric(factor_vector)
```

